---
title: "Extensions"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(bookdown)
library(stargazer)
library(tidyverse)
library(AER)
library(ggplot2)
library(readstata13)
library(spdep) 
library(tseries)
library(spatialreg)
```

```{r Loading}

# My loading code. 

load("Appendix_Data/kyrgyzstan.RData")
data <- table

# Shifting the victimization dummy to integer and switching 
# into a better binary. 

data$affected <- as.integer(data$affected)
data$affected <- data$affected - 1
data$pd_in <- as.integer(data$pd_in)
data$pd_out <- as.integer(data$pd_out)

```

```{r Uzbek Table Confounder Extension}

# Here I'm just creating my uzbek subset of the data. 
# The authors used base R so I decided to follow it too. 

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]

# Here I'm just scaling my variables and creating the cooperation
# index that is used throughout the paper. 

data_uzbek$pd_in_scale <- scale(data_uzbek$pd_in)
data_uzbek$dg_in_scale <- scale(data_uzbek$dg_in)
data_uzbek$pd_out_scale <- scale(data_uzbek$pd_out)
data_uzbek$dg_out_scale <- scale(data_uzbek$dg_out)
data_uzbek$cooperation_index <- rowSums(cbind(data_uzbek$pd_in_scale, 
                                              data_uzbek$dg_in_scale, 
                                              data_uzbek$pd_out_scale, 
                                              data_uzbek$dg_out_scale), na.rm=T)/4

# Now I'm separating the common employer variable because I thought 
# it would be more interesting to separate it into each ethnicity.

y <- data_uzbek %>%
  mutate(comm_employer = case_when(comm_employer == 1 ~ "Kyrgyz",
                                   comm_employer == 4 ~ "Other", 
                                   comm_employer == -1 ~ "Unemployed",
                                   comm_employer == 2 ~ "Uzbek", 
                                   comm_employer == 3 ~ "Russian"))

# Just placing them in the order I'd like.

y$comm_employer <- factor(y$comm_employer, levels = c("Kyrgyz", "Uzbek", "Russian", "Unemployed", "Other"))

# First OLS linear regressions for the confounders I wanted to explore. 

model1_Uzbek <- lm(pd_in_scale ~ affected + comm_lang_use  + education +  comm_employer, data=y)
model2_Uzbek <- lm(dg_in_scale ~ affected + comm_lang_use + education + comm_employer, data=y)
model3_Uzbek <- lm(pd_out_scale ~ affected + comm_lang_use +  education +  comm_employer, data=y)
model4_Uzbek <- lm(dg_out_scale ~ affected + comm_lang_use + education +  comm_employer, data=y)
model5_Uzbek <- lm(cooperation_index ~ affected + comm_lang_use + education + comm_employer, data=y)
```


\begin{center}
\textbf{Table 1: Uzbek Confounders}

```{r Table 1, results = "asis"}

# The table is way too wide without using scalebox here. 

cat("\\scalebox{.59}{")

# First table, but I made some changes to labels, font size, etc. 


stargazer(model1_Uzbek, model2_Uzbek, model3_Uzbek, model4_Uzbek, model5_Uzbek,
          covariate.labels = c("Destruction", "Common Language Usage", "Education", "Kyrgyz Employer", "Uzbek Employer", "Russian Employer", "Unemployed", "Constant"),
          dep.var.labels = c("Prisoner's Dilemma (In-Group)", "Dictator Game (In-Group)", "Prisoner's Dilemma (Out-Group)", "Dictator Game (Out-Group)" , "Cooperation-Index"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          single.row = TRUE, 
          font.size = NULL,
          column.sep.width = "1pt",
          header = FALSE, type = 'latex', float = FALSE)

# End of the scalebox

cat("}") 
```

\end{center}

\hfill\break
\hfill\break



\pagebreak

```{r Table 2}

# Now I wanted to isolate for just common language usage but also to check the interaction effect
# between it and the victimization dummy. 

model6_Uzbek <- lm(pd_in_scale ~ affected + comm_lang_use + affected * comm_lang_use, data=data_uzbek)
model7_Uzbek <- lm(dg_in_scale ~ affected + comm_lang_use + affected * comm_lang_use, data=data_uzbek)
model8_Uzbek <- lm(pd_out_scale ~ affected + comm_lang_use + affected * comm_lang_use, data=data_uzbek)
model9_Uzbek <- lm(dg_out_scale ~ affected + comm_lang_use + affected * comm_lang_use, data=data_uzbek)
model10_Uzbek <- lm(cooperation_index ~ affected + comm_lang_use + affected * comm_lang_use, data=data_uzbek)
```


\begin{center}
\textbf{Table 2: Uzbek Victimization and Common Language Usage Interaction}

```{r Table 2 Stargazer, results = "asis"}

# Same deal as before with scalebox. 

cat("\\scalebox{.59}{")

# Essentially the same code here as well for Table 2.

stargazer(model6_Uzbek, model7_Uzbek, model8_Uzbek, model9_Uzbek, model10_Uzbek,
          covariate.labels = c("Destruction", "Common Language Usage", "Interaction", "Constant"),
          dep.var.labels = c("Prisoner's Dilemma (In-Group)", "Dictator Game (In-Group)", "Prisoner's Dilemma (Out-Group)", "Dictator Game (Out-Group)" , "Cooperation-Index"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          single.row = TRUE, 
          font.size = NULL,
          column.sep.width = "1pt",
          header = FALSE, type = 'latex', float = FALSE)

# End scalebox.

cat("}") 
```


\end{center}

\hfill\break
\hfill\break


\pagebreak


```{r Starting Kyrgyz Data Tweaks}

# This is for the later regression table 

data$social_cap_retro <- data$leadership

# Now I'm just making a new subset of the data but for the Kyrgyz sample.
# I tried to keep the code the same as it was for the Uzbek sample.
# Same scaling and same cooperation index too. 

data_kyrgyz <- data[which(data$ethnicity=="Kyrgyz"),]

data_kyrgyz$pd_in_scale <- scale(data_kyrgyz$pd_in)
data_kyrgyz$dg_in_scale <- scale(data_kyrgyz$dg_in)
data_kyrgyz$pd_out_scale <- scale(data_kyrgyz$pd_out)
data_kyrgyz$dg_out_scale <- scale(data_kyrgyz$dg_out)
data_kyrgyz$cooperation_index <- rowSums(cbind(data_kyrgyz$pd_in_scale, 
                                              data_kyrgyz$dg_in_scale, 
                                              data_kyrgyz$pd_out_scale, 
                                              data_kyrgyz$dg_out_scale), na.rm=T)/4


```

```{r Figure 5 Kyrgyz Data}

# New basic OLS regressions but for the Kyrgyz.  

model1_Kyrgyz <- lm(pd_in_scale ~ affected, data=data_kyrgyz)
model2_Kyrgyz <- lm(dg_in_scale ~ affected, data=data_kyrgyz)
model3_Kyrgyz <- lm(pd_out_scale ~ affected, data=data_kyrgyz)
model4_Kyrgyz <- lm(dg_out_scale ~ affected, data=data_kyrgyz)
model5_Kyrgyz <- lm(cooperation_index ~ affected, data=data_kyrgyz)


# Now I'm using those regressions to create larger model frames that 
# have the information I need in a data frame. This will help for the graph
# later. 

model1Frame <- data.frame(Variable = rownames(summary(model1_Kyrgyz)$coef),
                          Coefficient = summary(model1_Kyrgyz)$coef[, 1],
                          SE = summary(model1_Kyrgyz)$coef[, 2],
                          modelName = "Prisoner's Dilemma ingroup")[2,]
model2Frame <- data.frame(Variable = rownames(summary(model2_Kyrgyz)$coef),
                          Coefficient = summary(model2_Kyrgyz)$coef[, 1],
                          SE = summary(model2_Kyrgyz)$coef[, 2],
                          modelName = "Dictator Game ingroup")[2,]
model3Frame <- data.frame(Variable = rownames(summary(model3_Kyrgyz)$coef),
                          Coefficient = summary(model3_Kyrgyz)$coef[, 1],
                          SE = summary(model3_Kyrgyz)$coef[, 2],
                          modelName = "Prisoner's Dilemma outgroup")[2,]
model4Frame <- data.frame(Variable = rownames(summary(model4_Kyrgyz)$coef),
                          Coefficient = summary(model4_Kyrgyz)$coef[, 1],
                          SE = summary(model4_Kyrgyz)$coef[, 2],
                          modelName = "Dictator Game outgroup")[2,]
model5Frame <- data.frame(Variable = rownames(summary(model5_Kyrgyz)$coef),
                          Coefficient = summary(model5_Kyrgyz)$coef[, 1],
                          SE = summary(model5_Kyrgyz)$coef[, 2],
                          modelName = "Index")[2,]

# Time to add them together, put them in the order I want, and rename them. 


allModelFrame <- data.frame(rbind(model1Frame, model2Frame, model3Frame, model4Frame, model5Frame))
allModelFrame$Variable <- c(1,2,3,4, 5)
allModelFrame$Variable <- factor(allModelFrame$Variable, 
                                 labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", 
                                          "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", 
                                          "Prosociality  Index"))

levels(allModelFrame$Variable) <- gsub("  ", "\n", levels(allModelFrame$Variable))

# I want to set confidence intervals 
# at 90% and 95%.. 

interval1 <- -qnorm((1-0.90)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier

# And setting the colors. 

myColors <- c("#000000", "#000000", "#000000", "#000000", "#000000")

# This is mostly the original author's code, but its very straight 
# forward ggplot code that just adds in all the details I need. 

figure1 <- ggplot(allModelFrame, aes(colour = as.factor(Variable))) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                     ymax = Coefficient + SE*interval1),
                 lwd = 1, position = position_dodge(width = 1/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                      ymax = Coefficient + SE*interval2),
                  lwd = 1/4, position = position_dodge(width = 1/2),
                  shape = 21, fill = "WHITE") + 
  coord_flip(ylim = c(-1,1)) + theme_bw() +
  scale_y_continuous(breaks = c(-1, -0.75, -0.5, -0.25, 0.0, 0.25, 0.5, 0.75, 1)) +
  theme(legend.position="none") + 
  ylab("")  + xlab("") +     
  scale_color_manual(values=myColors) +   
  theme(text = element_text(size=12)) +
  theme(plot.title = element_text(hjust = 0.5))
```


\begin{center}
\textbf{Model 1:  Kyrgyz Prosocial Behavior}

```{r Figure 5 Kyrgyz Data Output, fig.align="center"}

# Printing the first Kyrgyz figure. 

figure1
```

\end{center}


\pagebreak

```{r Kyrgyz Table Extension, include=FALSE}

# More OLS regressions but now to check for the original authors' confounders.  

model6_Kyrgyz <- lm(pd_in_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_kyrgyz)
model7_Kyrgyz <- lm(dg_in_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_kyrgyz)
model8_Kyrgyz <- lm(pd_out_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_kyrgyz)
model9_Kyrgyz <- lm(dg_out_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_kyrgyz)
model10_Kyrgyz <- lm(cooperation_index ~ affected + economy_index + state_index + 
                     social_cap_retro + access_index + aj_vote_share, data=data_kyrgyz)
```

\begin{center}
\textbf{Table 3: Kyrgyz Confounders}

```{r Kyrgyz Table Extension Stargazer, results = "asis"}

# Same deal as the two stargazer charts before. Same scalebox and same
# detail code. 

cat("\\scalebox{.59}{")

stargazer(model6_Kyrgyz, model7_Kyrgyz, model8_Kyrgyz, model9_Kyrgyz, model10_Kyrgyz,
          covariate.labels = c("Destruction", "Wealth index", "State capacity index", "Community policing index", "Accessibility index", "AJ %"),
          dep.var.labels = c("Prisoner's Dilemma (In-Group)", "Dictator Game (In-Group)", "Prisoner's Dilemma (Out-Group)", "Dictator Game (Out-Group)" , "Cooperation-Index"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          single.row = TRUE, 
          font.size = NULL,
          column.sep.width = "1pt",
          header = FALSE, type = 'latex', float = FALSE)

cat("}") 

```

\end{center}

\hfill\break
\hfill\break


\pagebreak


```{r Kyrygz Prosocial Instrument}

# Creating a distance variable like the authors. 

data$distance <- data$apc_min_distance

# And now I'm setting up like they did too. 

data_kyrgyz$distance <- 1-data_kyrgyz$apc_min_distance
dataAgg <- aggregate(data_kyrgyz[,c("affected", "distance")], 
                     list(data_kyrgyz$id_psu),
                     mean)

# Here are a new series of regressions separated into pairs of OLS and IV reg regressions. 
# Each will test the instrument variable and then use an IV reg to do the victimization
# dummy and the instrument. This is repeated for every index. 

model11_Kyrgyz <- lm(pd_in_scale ~ distance , data=data_kyrgyz)
model1_IV <- ivreg(pd_in_scale ~ affected | distance, data = data_kyrgyz)

model12_Kyrgyz <- lm(dg_in_scale ~ distance , data=data_kyrgyz)
model2_IV <- ivreg(dg_in_scale ~ affected | distance , data = data_kyrgyz)

model13_Kyrgyz <- lm(pd_out_scale ~ distance , data=data_kyrgyz)
model3_IV <- ivreg(pd_out_scale ~ affected  | distance , data = data_kyrgyz)

model14_Kyrgyz <- lm(dg_out_scale ~ distance , data=data_kyrgyz)
model4__IV <- ivreg(dg_out_scale ~ affected  | distance , data = data_kyrgyz)

model15_Kyrgyz <- lm(cooperation_index ~ distance , data=data_kyrgyz)
model5_IV <- ivreg(cooperation_index ~ affected  | distance , data = data_kyrgyz)


# Same as before, I am grabbing all the necessary data from each model and putting
# it in a data frame that I can use to graph later. 

modelFrame_6 <- data.frame(Variable = rownames(summary(model11_Kyrgyz)$coef),
                           Coefficient = summary(model11_Kyrgyz)$coef[, 1],
                           SE = summary(model11_Kyrgyz)$coef[, 2],
                           modelName = "PD ingroup")[2,]
modelFrame_7 <- data.frame(Variable = rownames(summary(model12_Kyrgyz)$coef),
                           Coefficient = summary(model12_Kyrgyz)$coef[, 1],
                           SE = summary(model12_Kyrgyz)$coef[, 2],
                           modelName = "DG ingroup")[2,]
modelFrame_8 <- data.frame(Variable = rownames(summary(model13_Kyrgyz)$coef),
                           Coefficient = summary(model13_Kyrgyz)$coef[, 1],
                           SE = summary(model13_Kyrgyz)$coef[, 2],
                           modelName = "PD outgroup")[2,]
modelFrame_9 <- data.frame(Variable = rownames(summary(model14_Kyrgyz)$coef),
                           Coefficient = summary(model14_Kyrgyz)$coef[, 1],
                           SE = summary(model14_Kyrgyz)$coef[, 2],
                           modelName = "DG outgroup")[2,]
modelFrame_10 <- data.frame(Variable = rownames(summary(model15_Kyrgyz)$coef),
                           Coefficient = summary(model15_Kyrgyz)$coef[, 1],
                           SE = summary(model15_Kyrgyz)$coef[, 2],
                           modelName = "Index")[2,]
IV_modelFrame_1 <- data.frame(Variable = rownames(summary(model1_IV)$coef),
                           Coefficient = summary(model1_IV)$coef[, 1],
                           SE = summary(model1_IV)$coef[, 2],
                           modelName = "PD ingroup")[2,]
IV_modelFrame_2 <- data.frame(Variable = rownames(summary(model2_IV)$coef),
                           Coefficient = summary(model2_IV)$coef[, 1],
                           SE = summary(model2_IV)$coef[, 2],
                           modelName = "DG ingroup")[2,]
IV_modelFrame_3 <- data.frame(Variable = rownames(summary(model3_IV)$coef),
                           Coefficient = summary(model3_IV)$coef[, 1],
                           SE = summary(model3_IV)$coef[, 2],
                           modelName = "PD outgroup")[2,]
IV_modelFrame_4 <- data.frame(Variable = rownames(summary(model4__IV)$coef),
                           Coefficient = summary(model4__IV)$coef[, 1],
                           SE = summary(model4__IV)$coef[, 2],
                           modelName = "DG outgroup")[2,]
IV_modelFrame_5 <- data.frame(Variable = rownames(summary(model5_IV)$coef),
                           Coefficient = summary(model5_IV)$coef[, 1],
                           SE = summary(model5_IV)$coef[, 2],
                           modelName = "Index")[2,]

# Here I combine the OLS regression toggether, reorder them, and then give them better names. 

allModelFrame2 <- data.frame(rbind(modelFrame_6, modelFrame_7, modelFrame_8, modelFrame_9, modelFrame_10))
allModelFrame2$Variable <- c(1,2,3,4,5)
allModelFrame2$Variable <- factor(allModelFrame2$Variable, labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", "Prosociality-  index"))
levels(allModelFrame2$Variable) <- gsub("  ", "\n", levels(allModelFrame2$Variable))

# Same as above but now for the IV regs. 

allModelFrame3 <- data.frame(rbind(IV_modelFrame_1,IV_modelFrame_2, IV_modelFrame_3, IV_modelFrame_4, IV_modelFrame_5))
allModelFrame3$Variable <- c(1,2,3,4,5)
allModelFrame3$Variable <- factor(allModelFrame3$Variable, labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", "Prosociality-  index"))
levels(allModelFrame3$Variable) <- gsub("  ", "\n", levels(allModelFrame3$Variable))

# TIme to make a master grouping of all model frames. Also differing between the OLS and 2SLS regressions. 

allModelFrame2 <- rbind(allModelFrame2, allModelFrame3)
allModelFrame2$test <- rep(c("Instrument", "Instrument", "Instrument", "Instrument", "Instrument", "2SLS", "2SLS", "2SLS", "2SLS", "2SLS"))

# Settign the 90% and 95% confidence intervals 

interval1 <- -qnorm((1-0.90)/2)  
interval2 <- -qnorm((1-0.95)/2)  

# The authors used this to set a dodge position for 
# the graph. I used it too. 

pd = position_dodge(0.5)

# Now its the ggplot code that makes everything look good. 
# Nothing crazy here to be honest. I just used the author's code
# and fitted it to my needs. 

figure2 <- ggplot(allModelFrame2, aes(shape=test)) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                     ymax = Coefficient + SE*interval1),
                 lwd = 1, position = pd) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval2,
                     ymax = Coefficient + SE*interval2),
                 lwd = 1/4, position = pd) + 
  geom_point(aes(x = Variable, y = Coefficient, shape = test),
             position = pd,fill = "WHITE", size = 3) + 
  coord_flip(ylim = c(-1.5,1.5)) + theme_bw() + 
  theme(legend.position="bottom") + 
  scale_shape_manual(values = c(23, 24, 25), name ="") +
  ylab("")  + xlab("") +     
  theme(text = element_text(size=12))
```

\begin{center}
\textbf{Model 2: Kyrgyz Prosocial Behavior with Instrumental Variable}

```{r Output Prosocial Kyrgyz Instrument, fig.align="center"}

# Printing.

figure2
```

\end{center}
