---
title: "Replications of Original Figures"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Loading all libraries
# that I'll need. 

library(spdep) 
library(tseries)
library(spatialreg)
library(foreign)
library(plyr)
library(AER)
library(data.table)
library(gt)
library(stargazer)
library(tidyverse)
```

```{r Loading}

# My loading code. 

load("~/Prosocial_Behavior_Replication_Project/Appendix/Appendix_Data/kyrgyzstan.RData")
data <- table

```

\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break
\hfill\break

```{r, Figure 4}

# So I figured it would be easy to replicate
# thier Figure 4 even though they don't give
# any replicable code. I just make some
# columns and then use gt to make it look like
# thier table. 

f4_1 <- c("+", "-", "-", "+")
f4_2 <- c(60, 80, 20, 100)
f4_3 <- c(60, 80, 100, 20)
f4_4 <- c("-", "+", "-", "+")

figure4 <- data.frame(f4_1, f4_2, f4_3, f4_4) %>%
  gt() %>%
  cols_label("f4_1" = " ", "f4_2" = " ", "f4_3" = " ", "f4_4" = " ") %>%
  tab_spanner(
    label = "You", 
    columns = vars(
      f4_1, f4_2)
    ) %>%
  tab_spanner(
    label = "Partner", 
    columns = vars(
      f4_3, f4_4
    )
  )
```

\begin{center}

\textbf{Figure 4. Payoff Illustration in Prisoner's Dilemma}

\end{center}

```{r Figure 4 Output, fig.align="center"}

# Printing

figure4
```

\pagebreak

```{r Figure 5}

# Just shifting the data I  want to use later by making certain
# columns integers, specifically the affected 
# and prisoner dilemma columns. Oh and the affected
# - 1 bit is to shift the binary from 1 and 0s to
# 0 and -1s. 

data$affected <- as.integer(data$affected)
data$affected <- data$affected - 1
data$pd_in <- as.integer(data$pd_in)
data$pd_out <- as.integer(data$pd_out)


# Just want to grab the data for Uzbeks
# as opposed to including the data for Kyrgyz 
# respondents. 

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]


data_uzbek$pd_in_scale <- scale(data_uzbek$pd_in)
data_uzbek$dg_in_scale <- scale(data_uzbek$dg_in)
data_uzbek$pd_out_scale <- scale(data_uzbek$pd_out)
data_uzbek$dg_out_scale <- scale(data_uzbek$dg_out)
data_uzbek$cooperation_index <- rowSums(cbind(data_uzbek$pd_in_scale, 
                                              data_uzbek$dg_in_scale, 
                                              data_uzbek$pd_out_scale, 
                                              data_uzbek$dg_out_scale), na.rm=T)/4


# Alright I totally understand what's happening here. 
# They are just running an OLS regression on the variables
# that they made and scaled in the last step and trying
# to see the effect that the affected variable had on each
# of them in turn. 

model1 <- lm(pd_in_scale ~ affected, data=data_uzbek)
model2 <- lm(dg_in_scale ~ affected, data=data_uzbek)
model3 <- lm(pd_out_scale ~ affected, data=data_uzbek)
model4 <- lm(dg_out_scale ~ affected, data=data_uzbek)
model5 <- lm(cooperation_index ~ affected, data=data_uzbek)


# This all makes sense too. After running the regressions 
# the authors have 5 list type data, but they need to extract 
# the information that they want. It's kinda weird but I see that 
# using this code they are getting the Variable, Coefficient, 
# standard error, and name of test for each model. Cool. 

model1Frame <- data.frame(Variable = rownames(summary(model1)$coef),
                          Coefficient = summary(model1)$coef[, 1],
                          SE = summary(model1)$coef[, 2],
                          modelName = "Prisoner's Dilemma ingroup")[2,]
model2Frame <- data.frame(Variable = rownames(summary(model2)$coef),
                          Coefficient = summary(model2)$coef[, 1],
                          SE = summary(model2)$coef[, 2],
                          modelName = "Dictator Game ingroup")[2,]
model3Frame <- data.frame(Variable = rownames(summary(model3)$coef),
                          Coefficient = summary(model3)$coef[, 1],
                          SE = summary(model3)$coef[, 2],
                          modelName = "Prisoner's Dilemma outgroup")[2,]
model4Frame <- data.frame(Variable = rownames(summary(model4)$coef),
                          Coefficient = summary(model4)$coef[, 1],
                          SE = summary(model4)$coef[, 2],
                          modelName = "Dictator Game outgroup")[2,]
model5Frame <- data.frame(Variable = rownames(summary(model5)$coef),
                          Coefficient = summary(model5)$coef[, 1],
                          SE = summary(model5)$coef[, 2],
                          modelName = "Index")[2,]

# So now they want to put all those extracted models together
# in one dataframe. Cool. Checks out. They're using rbind to do taht
# giving them a numeric order, and then using factor to put them 
# in the order that they want. Not really sure what levels() does, 
# but it looks like it cleans up the variable names to make them 
# easier to graph later. 


allModelFrame <- data.frame(rbind(model1Frame, model2Frame, model3Frame, model4Frame, model5Frame))
allModelFrame$Variable <- c(1,2,3,4, 5)
allModelFrame$Variable <- factor(allModelFrame$Variable, 
                                 labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", 
                                          "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", 
                                          "Prosociality  Index"))
levels(allModelFrame$Variable) <- gsub("  ", "\n", levels(allModelFrame$Variable))

# Okay so they want to set confidence intervals 
# at 90% and 95%. Seems clear. 

interval1 <- -qnorm((1-0.90)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier

# They want all colors to be 00000, which is probably black right? 

myColors <- c("#000000", "#000000", "#000000", "#000000", "#000000")

# I understand ggplot so this is cool. A bunch of detail stuff such
# as adding a vertical dotted line at 0.00 mark. Then they make a 
# horizontal linerange for every variable with thier ranges being
# the SE * the confidence intervals calculated before. Then the points
# show the mean effect which is the SE times the 95% CI with some cool
# shapes added in for coolness. Switching up the y axis labels, setting
# the theme, setting the colors, getting rid of the ticks, and generally
# making things pretty. 

figure5 <- ggplot(allModelFrame, aes(colour = as.factor(Variable))) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, 
                     ymin = Coefficient - SE*interval1,
                     ymax = Coefficient + SE*interval1),
                     lwd = 1, position = position_dodge(width = 1/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, 
                      ymin = Coefficient - SE*interval2,
                      ymax = Coefficient + SE*interval2),
                      lwd = 1/4, position = position_dodge(width = 1/2),
                      shape = 21, fill = "WHITE") + 
  coord_flip(ylim = c(-0.8,0.2)) + 
  scale_y_continuous(labels = c("-0.75", "-0.50", "-0.25", "0.00", "0.2")) +
  theme_bw() + 
  theme(legend.position="none") + 
  ylab("")  + xlab("") +     
  scale_color_manual(values=myColors) +   
  theme(text = element_text(size=11), 
        plot.title = element_text(size = 10, face = "bold"), 
        plot.subtitle = element_text(size = 11, face = "italic")) +
  theme(plot.title = element_text(hjust = 0.5))

```


\begin{center}
\textbf{Figure 5. Effect of Riot on Prosocial Behavior}

```{r Figure 5 Output, fig.align="center"}

# Printing the figure.

figure5
```

\end{center}

\begin{center}
\textbf{Figure 5. Screenshot}
\end{center}
\begin{center}
\includegraphics{Figure_5_Screenshot.PNG}
\end{center}

\pagebreak


```{r Figure 6}

# Here is the typical prep work the authors always do

data$affected <- as.integer(data$affected)
data$affected <- data$affected - 1
data$pd_in <- as.integer(data$pd_in)
data$pd_out <- as.integer(data$pd_out)


# Also renaming

data$distance <- data$apc_min_distance

data$social_cap_retro <- data$leadership

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]

# Scaling

data_uzbek$pd_in_scale <- scale(data_uzbek$pd_in)
data_uzbek$dg_in_scale <- scale(data_uzbek$dg_in)
data_uzbek$pd_out_scale <- scale(data_uzbek$pd_out)
data_uzbek$dg_out_scale <- scale(data_uzbek$dg_out)
data_uzbek$cooperation_index <- rowSums(cbind(data_uzbek$pd_in_scale, 
                                              data_uzbek$dg_in_scale, 
                                              data_uzbek$pd_out_scale, 
                                              data_uzbek$dg_out_scale), na.rm=T)/4
# More renaming

data_uzbek$distance <- 1-data_uzbek$apc_min_distance
dataAgg <- aggregate(data_uzbek[,c("affected", "distance")], 
                     list(data_uzbek$id_psu),
                     mean)

# Now they are setting theirr two stages for the IV test

first_stage_ind <- lm(affected ~ distance, data=data_uzbek)
first_stage_psu <- lm(affected ~ distance, data=dataAgg)

# First rounds of regressions with ivreg and lm

model11 <- lm(pd_in_scale ~ distance , data=data_uzbek)
model12 <- ivreg(pd_in_scale ~ affected | distance, data = data_uzbek)
model21 <- lm(dg_in_scale ~ distance , data=data_uzbek)
model22 <- ivreg(dg_in_scale ~ affected | distance , data = data_uzbek)
model31 <- lm(pd_out_scale ~ distance , data=data_uzbek)
model32 <- ivreg(pd_out_scale ~ affected  | distance , data = data_uzbek)
model41 <- lm(dg_out_scale ~ distance , data=data_uzbek)
model42 <- ivreg(dg_out_scale ~ affected  | distance , data = data_uzbek)
model51 <- lm(cooperation_index ~ distance , data=data_uzbek)
model52 <- ivreg(cooperation_index ~ affected  | distance , data = data_uzbek)


# Agreggating

dataAgg <- aggregate(data_uzbek[,c("apc_min_distance", "distance", "pd_in_scale", "dg_in_scale", 
                                   "pd_out_scale", "dg_out_scale", "cooperation_index", "affected", 
                                   "economy_index", "state_index", "social_cap_retro")], 
                     list(data_uzbek$id_psu),
                     mean)
# Even more Renaming

names(dataAgg)[1] <- "psu"


# Dropping NAs

dataAgg <- dataAgg[!is.na(dataAgg$social_cap_retro),] 

# Normal regressions


model1 <- lm(pd_in_scale ~ distance , data=dataAgg)
model2 <- lm(dg_in_scale ~ distance , data=dataAgg)
model3 <- lm(pd_out_scale ~ distance , data=dataAgg)
model4 <- lm(dg_out_scale ~ distance , data=dataAgg)
model5 <- lm(cooperation_index ~ distance , data=dataAgg)

# Making the model frames for the graph later.

model11Frame <- data.frame(Variable = rownames(summary(model11)$coef),
                           Coefficient = summary(model11)$coef[, 1],
                           SE = summary(model11)$coef[, 2],
                           modelName = "PD ingroup")[2,]
model21Frame <- data.frame(Variable = rownames(summary(model21)$coef),
                           Coefficient = summary(model21)$coef[, 1],
                           SE = summary(model21)$coef[, 2],
                           modelName = "DG ingroup")[2,]
model31Frame <- data.frame(Variable = rownames(summary(model31)$coef),
                           Coefficient = summary(model31)$coef[, 1],
                           SE = summary(model31)$coef[, 2],
                           modelName = "PD outgroup")[2,]
model41Frame <- data.frame(Variable = rownames(summary(model41)$coef),
                           Coefficient = summary(model41)$coef[, 1],
                           SE = summary(model41)$coef[, 2],
                           modelName = "DG outgroup")[2,]
model51Frame <- data.frame(Variable = rownames(summary(model51)$coef),
                           Coefficient = summary(model51)$coef[, 1],
                           SE = summary(model51)$coef[, 2],
                           modelName = "Index")[2,]
model12Frame <- data.frame(Variable = rownames(summary(model12)$coef),
                           Coefficient = summary(model12)$coef[, 1],
                           SE = summary(model12)$coef[, 2],
                           modelName = "PD ingroup")[2,]
model22Frame <- data.frame(Variable = rownames(summary(model22)$coef),
                           Coefficient = summary(model22)$coef[, 1],
                           SE = summary(model22)$coef[, 2],
                           modelName = "DG ingroup")[2,]
model32Frame <- data.frame(Variable = rownames(summary(model32)$coef),
                           Coefficient = summary(model32)$coef[, 1],
                           SE = summary(model32)$coef[, 2],
                           modelName = "PD outgroup")[2,]
model42Frame <- data.frame(Variable = rownames(summary(model42)$coef),
                           Coefficient = summary(model42)$coef[, 1],
                           SE = summary(model42)$coef[, 2],
                           modelName = "DG outgroup")[2,]
model52Frame <- data.frame(Variable = rownames(summary(model52)$coef),
                           Coefficient = summary(model52)$coef[, 1],
                           SE = summary(model52)$coef[, 2],
                           modelName = "Index")[2,]

# So they wanted to bring all models done for
# the original data. And then arrange the order
# using factor. 

allModelFrame1 <- data.frame(rbind(model11Frame, model21Frame, model31Frame, model41Frame, model51Frame))
allModelFrame1$Variable <- c(1,2,3,4,5)
allModelFrame1$Variable <- factor(allModelFrame1$Variable, labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", "Prosociality-  index"))
levels(allModelFrame1$Variable) <- gsub("  ", "\n", levels(allModelFrame1$Variable))


# So now they want to combine all the models that have the spatial 
# component to them. 

allModelFrame2 <- data.frame(rbind(model12Frame, model22Frame, model32Frame, model42Frame, model52Frame))
allModelFrame2$Variable <- c(1,2,3,4,5)
allModelFrame2$Variable <- factor(allModelFrame2$Variable, labels=c("Prisoner's Dilemma  Ingroup", "Dictator Game  Ingroup", "Prisoner's Dilemma  Outgroup", "Dictator Game  Outgroup", "Prosociality-  index"))
levels(allModelFrame2$Variable) <- gsub("  ", "\n", levels(allModelFrame2$Variable))


# allModelFram <- rbind(allModelFrame1, allModelFrame2, allModelFrame3)
# allModelFram$matrix_style <- rep(c("Instrument", "2SLS", "Instrument (SAM)"),each=5)


allModelFram <- rbind(allModelFrame1, allModelFrame2)
allModelFram$test <- rep(c("Instrument", "Instrument", "Instrument", "Instrument", "Instrument", "2SLS", "2SLS", "2SLS", "2SLS", "2SLS"))


interval1 <- -qnorm((1-0.90)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier


# They set up their dodge position for the graph.

pd = position_dodge(0.5)


# Typical ggplot code.

figure6 <- ggplot(allModelFram, aes(shape=test)) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                     ymax = Coefficient + SE*interval1),
                 lwd = 1, position = pd) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval2,
                     ymax = Coefficient + SE*interval2),
                 lwd = 1/4, position = pd) + 
  geom_point(aes(x = Variable, y = Coefficient, shape = test),
             position = pd,fill = "WHITE", size = 3) + 
  coord_flip(ylim = c(-0.95,0.22)) + theme_bw() + 
  theme(legend.position="bottom") + 
  scale_shape_manual(values = c(23, 24, 25), name ="") +
  ylab("")  + xlab("") +     
  theme(text = element_text(size=18))
```

\begin{center}
\textbf{Figure 6.  Effect of Riot Destruction on Prosocial Behavior (IV)}

```{r Figure 6 Output, fig.align='center'}

# Printing

figure6
```

\end{center}

\pagebreak

```{r Figure 8, cache=TRUE, include=FALSE}

# Like I said before the scaling code doesn't change
# in between the figures so I won't comment on it 
# much anymore. This is just thier scaling and making
# the cooperation index var.

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]
data_uzbek$pd_in_scale <- scale(data_uzbek$pd_in)
data_uzbek$dg_in_scale <- scale(data_uzbek$dg_in)
data_uzbek$pd_out_scale <- scale(data_uzbek$pd_out)
data_uzbek$dg_out_scale <- scale(data_uzbek$dg_out)
data_uzbek$cooperation_index <- rowSums(cbind(data_uzbek$pd_in_scale, data_uzbek$dg_in_scale, data_uzbek$pd_out_scale, data_uzbek$dg_out_scale), na.rm=T)/4
data_uzbek$distance <- data_uzbek$apc_min_distance


# So the first lin eis a typical regression. The third
# is also a typical regression but for the instrument i.e.
# distance to apc vehicle. The second is an instrumental 
# variable regression. I understand what it is by reading
# the notes on it, but I'll need more time to get
# what it is doing here. 

ols <- lm(cooperation_index ~ affected, data = data_uzbek)
iv <- ivreg(cooperation_index ~ affected | distance , data = data_uzbek)
instrument <- lm(cooperation_index ~ distance , data = data_uzbek)

# So here the authors wanted to randomize APC locations to 
# test the affect they have on figure 6. I get that. So they load in 
# the distance data they chose for that. Their note says 
# "Insheet distances from any given PSU to 9500 randomly chosen APC locations"

DistMat <- as.data.frame(read.csv("~/Prosocial_Behavior_Replication_Project/Appendix/Appendix_Data/distances_ri.csv", header = TRUE, sep =","))[-1]

# So every column in DistMat has an X in it. Here they really just want
# to get rid of those. 

colnames(DistMat) <- c(na.omit(as.numeric(unlist(strsplit(as.matrix(colnames(DistMat)), "X"))))) 

# Now they want to obtain PSU names from 
# the survey data as character to match to DistMat

psus <- c(as.character(unique(data_uzbek$id_psu)))

# Here they want to reduce distance matrix to 
# entries for PSUs where they sampled Uzbek respondents

sample_psus <- names(DistMat)[(names(DistMat) %in% psus)]
DistMat <- DistMat[, sample_psus]

# So the authors also had data about whether these apc locations
# were east of the Akbuura river or not. This is them loading it in 
# and then adding it to their other data. 

eoa <- as.data.frame(read.csv("~/Prosocial_Behavior_Replication_Project/Appendix/Appendix_Data/ri_east_of_akbuura.csv", header = TRUE))[2]
DistMat$eoa <-eoa

# Now they want to create matrices of whether the locations were
# east or west of the Akbuura river. Then they wanted to 
# make them into separate dataframes. 

DistMat_east <- subset(DistMat, eoa==1)
DistMat_west <- subset(DistMat, eoa==0)
DistMat = subset(DistMat, select = -c(eoa) )
DistMat_west = subset(DistMat_west, select = -c(eoa) )
DistMat_east = subset(DistMat_east, select = -c(eoa) )

# Setting the seed for some randomization but also
# they wanted to fill up the vectors so that they both have legnths of 
# 5000 apparently. 

set.seed(1000)
DistMat_east <- rbind(DistMat_east, DistMat_east[sample(169), ])
set.seed(1000)
DistMat_west <- rbind(DistMat_west, DistMat_west[sample(331),])

# I get this step now. They want to shuffle thier
# data sets from before. 

set.seed(1000)
DistMat_east <- DistMat_east[sample(nrow(DistMat_east)),]
set.seed(1000)
DistMat_west <- DistMat_west[sample(nrow(DistMat_west)),]

# They are creating a randome samling with replacment data frame. 

n <- 10000
set.seed(1000)
rand_vals <- sample(c(1:5000), n, replace = TRUE)

# They want to "store coefficient in vector
# with elements equal to draws" according to thier
# code comments. I follow that. 

estim <- matrix(0, nrow=n, ncol=1)

# Okay so this is tricky right, but they are using foor
# loop to loop through all values. 

j <- 0
for (i in rand_vals){
  j <- j + 1
  
   
# Then they are taking a distance from both east and west, transposing,
# finding minimum distance and then adding a column for matching. 
  
  dist_i_west <- as.data.frame(t(DistMat_west[i,]))
  dist_i_east <- as.data.frame(t(DistMat_east[i,]))
  dist_i <- cbind(dist_i_west, dist_i_east)

# Then they choose the APC location in east or west that is closest to thier
# interview location, according to thier notes. 
  
  dist_i <- as.data.frame(apply(dist_i, 1, FUN=min))
  dist_i <- setDT(dist_i, keep.rownames = TRUE)
  colnames(dist_i)=c("id_psu", "drivedist")
  
# Then they merge the data. 
  
  combinedData <- join(data_uzbek, dist_i, by='id_psu', type='left', match='all')
  
# Then they run a regression on the coperation index and 
# the new locations. 
  
  ivest_i <- lm(cooperation_index ~ drivedist, data=combinedData)  
  
# Then they save the results somehow and merge them 
# to the coef matrix they made earlier. 
  
  estim[j,1] <- estim[j,1] + coef(ivest_i)[2] 
}

# Okay I'm back to understanding things. So here they are shifting their
# dat to negative again. Making it a data frame and finding the mean. 

estim <- estim*-1  #convert to negative scale "closeness to barracks"
data_combined <- as.data.frame(estim)
mean(estim)

# Graphing code is graphic code. They make a density plot. 
# Then they add in a bunch of details like a vertical line
# and such. 

figure8 <- ggplot(data_combined, aes(x=V1)) +  
  geom_density(bw = 0.02) +
  theme_bw() + 
  ylab("Density")  + xlab("Estimate") +     
  theme(text = element_text(size=11)) +
  scale_x_continuous(limits = c(-0.2,0.2)) + 
  geom_vline(xintercept=instrument$coefficients[2]*-1, linetype=2, color = "grey") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```


\begin{center}
\textbf{Figure 8. Randomization Inference}

```{r Figure 8 Output, fig.align="center"}

# Time to make the actual graph. 

figure8
```

\end{center}

\pagebreak


```{r Figure 9}

# They're just making affected an 
# integer again and then shifting the
# binary state to negative 1 and 0.

data$affected <- as.integer(data$affected)
data$affected <- data$affected - 1

# Now they subset the data. 

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]

# This bit of the paper is an exploration of whether
# the people who were affected by the riots actually
# had more damages than other types. So they run the 
# OLS regressions on each type of loss. 

model1 <- lm(losses_1 ~ affected, data=data_uzbek)
model2 <- lm(losses_2 ~ affected, data=data_uzbek)
model3 <- lm(losses_3 ~ affected, data=data_uzbek)
model4 <- lm(losses_4 ~ affected, data=data_uzbek)
model5 <- lm(losses_5 ~ affected, data=data_uzbek)


# Here they just want to grab their coefficients from 
# the regressions they ran earlier. 

model1Frame <- data.frame(Variable = rownames(summary(model1)$coef),
                          Coefficient = summary(model1)$coef[, 1],
                          SE = summary(model1)$coef[, 2],
                          modelName = "Car")[2,]
model2Frame <- data.frame(Variable = rownames(summary(model2)$coef),
                          Coefficient = summary(model2)$coef[, 1],
                          SE = summary(model2)$coef[, 2],
                          modelName = "TV")[2,]
model3Frame <- data.frame(Variable = rownames(summary(model3)$coef),
                          Coefficient = summary(model3)$coef[, 1],
                          SE = summary(model3)$coef[, 2],
                          modelName = "House")[2,]
model4Frame <- data.frame(Variable = rownames(summary(model4)$coef),
                          Coefficient = summary(model4)$coef[, 1],
                          SE = summary(model4)$coef[, 2],
                          modelName = "Money")[2,]
model5Frame <- data.frame(Variable = rownames(summary(model5)$coef),
                          Coefficient = summary(model5)$coef[, 1],
                          SE = summary(model5)$coef[, 2],
                          modelName = "Business")[2,]

# Here they once again want to combine all thier data into one. 
# They also want to list them in a particular order. 

allModelFrame <- data.frame(rbind(model1Frame, model2Frame, model3Frame, model4Frame, model5Frame))
allModelFrame$Variable <- c(1,2,3,4, 5)
allModelFrame$Variable <- factor(allModelFrame$Variable, labels=c("Car", "TV", "House", "Money", "Business"))
levels(allModelFrame$Variable) <- gsub("  ", "\n", levels(allModelFrame$Variable))

# Now they want to calculat the 90 and 95 CIs. 

interval1 <- -qnorm((1-0.90)/2)  # 90% multiplier
interval2 <- -qnorm((1-0.95)/2)  # 95% multiplier

# And then its another round of color setting. 

myColors <- c("#000000", "#000000", "#000000", "#000000", "#000000")


# Same graphing code from Figure 5 and 6. Refer to my comments
# on Figure 5 for a more detailed analysis of what's happening. 

figure9 <- ggplot(allModelFrame, aes(colour = as.factor(Variable))) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = Coefficient - SE*interval1,
                     ymax = Coefficient + SE*interval1),
                 lwd = 1, position = position_dodge(width = 1/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Coefficient - SE*interval2,
                      ymax = Coefficient + SE*interval2),
                  lwd = 1/4, position = position_dodge(width = 1/2),
                  shape = 21, fill = "WHITE") + 
  coord_flip(ylim = c(-0.1,0.3)) + theme_bw() + 
  theme(legend.position="none") + 
  #ggtitle("Cooperation among Uzbeks") +  
  ylab("")  + xlab("") +     
  scale_color_manual(values=myColors) +   
  theme(text = element_text(size=11)) +
  theme(plot.title = element_text(hjust = 0.5))
```

\begin{center}
\textbf{Figure 9. Effect of Riot Destruction on Losses}

```{r Figure 9 Output, fig.align='center'}

# output

figure9
```

\end{center}

\pagebreak


```{r Table 1, include=FALSE}

# Same cleaning code that they've done
# for all figures. Its just as.integer commands
# and shifting the binary.

data$affected <- as.integer(data$affected)
data$affected <- data$affected - 1
data$pd_in <- as.integer(data$pd_in)
data$pd_out <- as.integer(data$pd_out)


# They wanted to rename a variable here. 

data$social_cap_retro <- data$leadership

# Subsetting time as per usual.

data_uzbek <- data[which(data$ethnicity=="Uzbek"),]

# And once more they wanted to scale everything. 
# Remind me to ask Alice to clarify what this does 
# in simple terms. I think I get it but I want to 
# make sure. 

data_uzbek$pd_in_scale <- scale(data_uzbek$pd_in)
data_uzbek$dg_in_scale <- scale(data_uzbek$dg_in)
data_uzbek$pd_out_scale <- scale(data_uzbek$pd_out)
data_uzbek$dg_out_scale <- scale(data_uzbek$dg_out)
data_uzbek$cooperation_index <- rowSums(cbind(data_uzbek$pd_in_scale, 
                                              data_uzbek$dg_in_scale, 
                                              data_uzbek$pd_out_scale, 
                                              data_uzbek$dg_out_scale), na.rm=T)/4

# So many multivariate linear regressions. So this 
# is their table info which requires the prisoner dilemma, 
# dictator game, and cooperation index to be regressed by 
# a bushel of variables. Here is where I'd like to do some
# playing around when its my turn to make changes. 

model1 <- lm(pd_in_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_uzbek)
model2 <- lm(dg_in_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_uzbek)
model3 <- lm(pd_out_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_uzbek)
model4 <- lm(dg_out_scale ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_uzbek)
model5 <- lm(cooperation_index ~ affected + economy_index + state_index + social_cap_retro + access_index + aj_vote_share, data=data_uzbek)

# I actually don't know why they are
# running a summary on every model but
# I assume they need to in order to run
# the stargazer. 

summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
```

\begin{center}
\textbf{Table 1}
\end{center}

```{r Table 1 Stargazer, results = "asis"}

# Alright so this is weird. I know they are using stargazer 
# to make the really nice looking table in the paper. I don't know
# how this code works though. I can't seem to replicate it myself.
# This is something else I'll need Alice's help with. Or I just need 
# enough time to figure out how stargazer works. 

cat("\\scalebox{.55}{")

stargazer(model1, model2, model3, model4, model5,
          covariate.labels = c("Destruction", "Wealth index", "State capacity index", "Community policing index", "Accessibility index", "AJ %"),
          dep.var.labels = c("Cooperation in Prisoner's Dilemma", "Investment in Dictator Game", "Cooperation in Prisoner's Dilemma", "Investment in Dictator Game" , "Cooperation-Index"),
          star.char = c("*", "**", "***"),
          title = "Table 1: Effect of Destruction on Prosocial Behavior (controlling for confounders and mobilization)",
          star.cutoffs = c(0.05, 0.01, 0.001), type = 'latex', float = FALSE)


cat("}") 
```

